---
title: 'Individual Assignment #2'
Name: Muskaan Singhania
EID: ms88283
output:
  html_document:
    df_print: paged
  pdf_document: default
editor_options:
  markdown:
    wrap: 72
---

------------------------------------------------------------------------

<center>

## Assignment #2: ARIMA Laboratory

### Name: Muskaan Singhania

### EID: ms88283

#### Due: Nov. 29 (Before Class)

#### (40 points)

</center>

------------------------------------------------------------------------

### Part I. Estimating Growth Potential and Capacity Utilization

Suppose you are working for a firm in the restaurant business looking
into the possibility of starting operations in Australia. Your company
has already narrowed its focus to five states: (i) Queensland, (ii)
Victoria, (iii) New South Wales, (iv) Western Australia, and (v) the
Australian Capital Territory. The decision of locations to start
operations depend on two factors:

(A) **Growth Potential:** More than the size of the market itself, the
    firm is interested in starting operations in locations with high
    growth rates. The reasoning behind this decision is that it is
    easier to gain a foothold in a market that is growing than in one
    that is stagnant.

(B) **Demand Variability:** There are two dimensions to demand
    variability. First, the change in mean demand from month to month
    over the year, i.e., the seasonality; and second, the volatility of
    the demand within each season. This is important as high levels of
    seasonality and high levels of uncertainty lead to reduced expected
    expected levels of capacity utilization and lower cash flows from
    operation.

To aid your analysis, we include in the code box below an ETS analysis
of the sales (turnover) of the aggregate restaurant industry in each
state. Please base your answers to question (1) and (2) on the results
obtained by the analysis below.

```{r, warning=FALSE, echo=FALSE, results = FALSE, message=FALSE}
library(fpp3)
```

```{r warning=FALSE}
R <- aus_retail %>%
  filter(Industry == "Cafes, restaurants and takeaway food services", 
         State == "Australian Capital Territory"|
           State == "Queensland" |
           State == "Victoria" |
           State == "Western Australia" |
           State == "New South Wales" ) %>%
  mutate(Sales = Turnover) %>%
  select(State, Sales)

R %>% autoplot(.var = Sales)

m <- R %>% model(me = ETS(Sales))

MC <- m %>% components() 

MC %>% filter(State == "Australian Capital Territory") %>% filter(Month >= ym("2017 Dec"))
MC %>% filter(State == "Queensland") %>% filter(Month >= ym("2017 Dec"))
MC %>% filter(State == "New South Wales") %>% filter(Month >= ym("2017 Dec"))
MC %>% filter(State == "Western Australia") %>% filter(Month >= ym("2017 Dec"))
MC %>% filter(State == "Victoria") %>% filter(Month >= ym("2017 Dec"))

MC %>% filter(State == "Australian Capital Territory") %>% autoplot()
MC %>% filter(State == "Queensland") %>% autoplot()
MC %>% filter(State == "New South Wales") %>% autoplot()
MC %>% filter(State == "Western Australia") %>% autoplot()
MC %>% filter(State == "Victoria") %>% autoplot()
```

1.  **What is the type of growth estimated by the models above for each
    state?**

Ans: Growth type for the aforementioned states are:

**Queensland**\
Model: ETS(M,Ad,M)\
Growth Type: Multiplicative error, Additive damped trend and
Multiplicative seasonality

**New South Wales**\
Model: ETS(M,A,M)\
Growth Type: Multiplicative error, Additive trend and Multiplicative
Seasonality

**Western Australia**\
Model: ETS(M,A,M)\
Growth Type: Multiplicative error, Additive trend and Multiplicative
Seasonality

**Australian Capital Territory**\
Model: ETS(M,A,M)\
Growth Type: Multiplicative error, Additive trend and Multiplicative
Seasonality

**Victoria** \
Model: ETS(M,Ad,M) \
Growth Type: Multiplicative error, Additive damped trend and
Multiplicative Seasonality

2.  **What are the values of the growth parameters (for each state) at
    the end of analysis period**?

Ans: The following are the values of the growth parameters:

**Queensland\
**Level: 709.308\
Trend: 0.118\
Seasonality: 1.110

**New South Wales\
**Level: 1332.941\
Trend: 3.468\
Seasonality: 1.141

**Western Australia\
**Level: 483.581\
Trend: 1.186\
Seasonality: 1.069

**Australian Capital Territory\
**Level: 65.415\
Trend: 0.168\
Seasonality: 1.097

**Victoria** \
Level: 946.492\
Trend: 2.269\
Seasonality: 1.134

3.  What is the growth rate (expressed as a percentage) of sales
    experienced by each state over the last twelve months? Calculate
    this as the percent change in the de-seasonalized level of demand
    estimated over the last twelve months.

```{r warning=FALSE}
MC %>%                                   
  group_by(State) %>%
  mutate(growth_rate = ((level / lag(level,12)) -1)*100) %>%
  filter(Month == ym("2018 Dec")) %>%
  as_tibble %>%
  select(State, growth_rate) -> mc_growth

mc_growth
```

4.  One measure of operational risk is the effect of variability of mean
    demand from season to season on capacity utilization. A simple way
    to estimate this is to calculate for each of the five states
    $D_{MAX} = \max_m D_m$ where the index $m$ takes values
    corresponding to the last twelve months. That is, $D_{MAX}$ is the
    maximum mean level of demand fitted for the last twelve months. Then
    calculate the monthly metric of mean-forecast-based capacity
    utilization for each month as
    $$ U_m = \frac{D_m}{D_{MAX}} \times 100,$$ then, using the monthly
    mean-based capacity utilization obtain the average
    mean-forecast-based utilization as $MU = mean(U_m)$ Report the
    utilization calculation for each of the five states. Summarize your
    analysis of sales growth potential and mean-variability with a table
    indicating the annual growth rate and annual average mean-base
    capacity utilization for each state. Management wants you to pick
    three of these five states to start operations base only on your
    analysis. explain your reasoning. Are there any states that are
    dominated by other states based only on the growth vs. utilization
    metrics? Explain.

```{r warning=FALSE}
MC %>%                                   
  group_by(State) %>%
  mutate(mean_dem = (lag(level,1)+lag(slope,1))*lag(season,12)) %>%
  filter(Month >= ym("2018 Jan")) %>%
  mutate(max_dem = (max(mean_dem))) %>%
  mutate(util = (mean_dem/max_dem)*100) %>%
  mutate('Average Capacity Utilisation' = mean(util)) -> mc_util
mc_util
```

```{r}
mc_util %>%  
  as_tibble %>%
  group_by(State) %>%
  summarise('Average Capacity Utilisation' = mean(util)) -> mc_util_fin

mc_util_fin
```

```{r warning=FALSE}
mc_growth$'Average Capacity Utilisation' <- mc_util_fin$'Average Capacity Utilisation'

mc_growth$ranking_state = rank(-mc_growth$growth_rate)
mc_growth$util_rank = rank(-mc_growth$'Average Capacity Utilisation')
mc_growth$Avg_Rank = mc_growth$ranking_state*0.5 + mc_growth$util_rank*0.5
mc_growth
```

Ranking based on growth metric:

1.  Australian Capital Territory
2.  Victoria
3.  New South Wales
4.  Western Australia
5.  Queensland

Ranking based on utilization metric:

1.  Western Australia
2.  Queensland
3.  Australian Capital Territory
4.  New South Wales
5.  Victoria

From the above outputted table, the selected states are **Australian
Capital Territory, Western Australia and New South Wales**

This selection has been made based on:

1.  Average Rank column

2.  We see that even though Victoria has promising growth potential, it
    is lacking when it comes to utilization

3.  Similarly, Queensland shows promising utilization but lacking the
    growth potential

4.  Hence, the most intuitive pick for the third state would be New
    South Wales

### Part II. Estimating Downside Risk in Capacity Utilization

After looking at your analysis and considering a number of additional
factors not included in your analysis, management decided to narrow
their prospecting to New South Wales, Western Australia and Victoria,
and are asking for a more detailed analysis of the capacity utilization
risk. To estimate this risk, they are asking you to use the actual
state-wide sales level as an index of what would be the company's sales,
and assume that the actual system capacity will be built as the 95%
quantile of the forecasted demand. Management is tasking you to estimate
the average capacity utilization and the downside capacity utilization
risk for each state. The following questions guide you through this
analysis:

5.  Using the training and testing sets specified below, fit the best
    ETS and ARIMA models for the sales in each of these three states.
    Comment on the selection of a forecasting model for each state based
    on the validity, accuracy and information criteria for each model.

```{r}
# Break into Training and Testing sets.

S <- R %>% 
  filter(State == "New South Wales" |
         State == "Western Australia" |
         State == "Victoria")

TR <- S %>% 
  filter(Month >= yearmonth("2000 Jan"),
         Month <= yearmonth("2017 Dec"))
TE <- S %>% 
  filter(Month >= yearmonth("2018 Jan"))

model_eval <- TR %>% model(ets_model = ETS(Sales),
                        arima_model = ARIMA(Sales))
model_eval %>% glance()
```

Based on AIC, AICc and BIC - Arima models seem to performing better for
all the three states

```{r}
forecast_mod <- model_eval %>% forecast(h = 12)

rbind(model_eval %>% accuracy(), 
            forecast_mod %>% accuracy(data = TE))
```

Based on Out-of-sample MAPE, Arima Model performs better for Victoria
and New South Wales whereas ETS performs better for Western Australia

After listening to your arguments, and considering other subjective
factors, your supervisor ask you to select the ARIMA model you obtained
for the states of Western Australia and Victoria, but she prefers the
ETS model for New South Whales. Use the above models to answer the
following questions.

6.  Fit the actual models selected as the best ARIMA and ETS (see above)
    and re-fit these models using all the available data (i.e, the **S**
    data set), and then prepare a 12-month ahead forecast for each
    state. Report the forecast and the 80% and 90% confidence intervals
    for each state.

```{r}

model_WA = S %>% filter(State=='Western Australia') %>% model(model_ar = ARIMA(Sales ~ pdq(2,0,0) + PDQ(0,1,2)))
    
model_Vic = S %>% filter(State=='Victoria') %>% model(model_ar = ARIMA(Sales ~ pdq(1,0,1) + PDQ(1,1,2)))

model_SW = S %>% filter(State=='New South Wales') %>% model(model_ets = ETS(Sales ~ error('M') + trend('Ad') +season('M')))
    
forecast_WA = model_WA %>% forecast(h=12)
forecast_Vic = model_Vic %>% forecast(h=12)
forecast_SW = model_SW %>% forecast(h=12)

f_agg = bind_rows(forecast_WA, forecast_Vic, forecast_SW)
f_agg %>% hilo(level =c(80,90)) %>%
  unpack_hilo("80%") %>% unpack_hilo("90%")
```

7.  Using the forecasting models in Question 6, assume that your company
    will build capacity up to 95% of the maximum demand forecast for the
    following 12 months. That is, where is the maximum 95% quantile of the demand forecasts for
    the following 12 months. Then obtain the downside risk capacity
    utilization risk as is the demand corresponding to the 5% quantile of
    the sales forecast, and then, using the monthly downside capacity
    utilization obtain the average downside utilization as
    Report the utilization calculation for each of
    the three states. 
```{r}
#Western Australia
WA_avg = f_agg %>% filter(State=='Western Australia') %>% mutate(Quant_95 = quantile(Sales, 0.95), Quant_05 = quantile(Sales, 0.05), CAP=max(Quant_95), DUR=Quant_05/CAP * 100) %>% as_tibble() %>%
  group_by(State) %>% summarise(DURmean = mean(DUR))

#Victoria
Vic_avg = f_agg %>% filter(State=='Victoria') %>% mutate(Quant_95 = quantile(Sales, 0.95), Quant_05 = quantile(Sales, 0.05), CAP=max(Quant_95), DUR=Quant_05/CAP * 100) %>% as_tibble() %>%
  group_by(State) %>% summarise(DURmean = mean(DUR))

#New South Wales
NSW_avg = f_agg %>% filter(State=='New South Wales') %>% mutate(Quant_95 = quantile(Sales, 0.95), Quant_05 = quantile(Sales, 0.05), CAP=max(Quant_95), DUR=Quant_05/CAP * 100)  %>% as_tibble() %>%
  group_by(State) %>% summarise(DURmean = mean(DUR))

#Aggregate
rbind(WA_avg, Vic_avg, NSW_avg)
```

8.  After examining your analysis in Question (7) management made two
    decisions: First, Building capacity up to the 95% quantile of demand
    was too considered too risky and affected expected profitability,
    and ask you to redefine the capacity at the 70% quantile. and second, they decided that the downside
    risk at the 5% quantile was to conservative, and ask you to
    re-calculate the figures you reported using a downside demand
    estimated at the 10% quantile of the demand forecast and repeat your
    calculations in Question 7. Comment on the likely effect of the
    capacity reduction decision on the capacity utilization at the
    median demand. Explain the difference with the
    utilization quantities estimated in Question (4)

```{r}
bind_rows(forecast_WA,forecast_Vic,forecast_SW) %>%
  mutate(Quant_70 = quantile(Sales, 0.70)) %>%
  group_by(State) %>%
  mutate(max_quant_70 = max(Quant_70)) %>%
  mutate(DUR = quantile(Sales, 0.10)/max_quant_70) %>%
  as_tibble %>%
  group_by(State) %>%
  summarise(Mean_DUR = mean(DUR)*100)
```

1.  Average downside utilization increase when the capacity was at 70%
    quantile and downside risk was raised to 10% from the previous value
    of 5%
2.  In conclusion, reduction in capacity led to increase in capacity
    utilization and median demand

```{r}
bind_rows(forecast_WA,forecast_Vic,forecast_SW) %>%
  mutate(Quant_70 = quantile(Sales, 0.70)) %>%
  group_by(State) %>%
  mutate(max_quant_70 = max(Quant_70)) %>%
  mutate(DUR = quantile(Sales, 0.50)/max_quant_70) %>%
  as_tibble %>%
  group_by(State) %>%
  summarise(Mean_DUR = mean(DUR)*100)
```

1.  Table above, mean capacity utilization at median demand with 70%
    quantile capacity
2.  Table in Q4, mean capacity utilization at mean demand with capacity
    equal to mean demand

Hence Q4 shows better utilization values.
